---
title: "GED dynamic tabs example"
author: "Anthony Davidson, Emily Stringer and Mark Gingrass (original content)"
date: "`r Sys.Date()`"
output:
   bookdown::html_document2:
      theme: journal
      highlight: tango
      df_print: paged
      toc: yes
      toc_depth: '3'
keep_md: TRUE
---

```{r echo = FALSE, warning=FALSE, message=FALSE}
library(DT)
library(tidyverse)
ged.min <- read.csv("data/random_ged_resample.csv") %>%
            mutate(site = factor(site))

levels(ged.min$site)
```

# Overview {.tabset}

Here are some old notes I found for creating dynamic tabs for a collection of sites. I have added notes to this document with a set of examples using the same site names but different data (just in case).

```{r echo = FALSE, warning=FALSE, message=FALSE}
 ppt <- ggplot(ged.min, aes(y = n, x = year, group = paste(site, year))) +
        geom_point() +
        geom_line() +
        facet_wrap(~site, scales = "free", ncol =2 ) +
        theme_bw()+ 
     theme(axis.text.x = element_text(angle = 90))

ppt
```

## Dynamic tabs

Dynamic tabs are an easy way to add a single dynamic component that does not require a server to support (e.g. Shiny apps). Dynamic tabs are controlled by creating a stored list of objects (in this case ggplots) using the following code after the desired heading `{.tabset}`. An extension of this is the style aspects attached to the tab using `{.tabset .tabpills}`.

## Insert iframe

This quick little shortcut helps with including dynamic content inside static web and html documents. You can also use `knitr::include_app` here in R code too but I find the html snippet below to work just as well inside a RMD file.

<iframe width="560" height="315" src="https://youtube.com/embed/KMTWjPLEolc" frameborder="0" allowfullscreen></iframe>

>NOTE: the iframe outputs do not show up currently in the rendered RStudio window. You need to `Open in Browser` in top left corner of popout viewer in RStudio.

## Tables in a static RMD 

It is possible to create interactive datatables uses the javascript library using htmlwidgets I think. Anyways, it works in a RMD file like so:

Talk about this data here. 

```{r echo = FALSE, warning= FALSE, message=FALSE}
#DT library
DT::datatable(ged.min)
```

## Including code in RMDs

There are two main ways to do this currently, `child = <RMD>, results = "asis"` in the code chunk heading and using source in the chunk itself. Here I have included the resampling code below using source. Note the R script is in the `./R/` folder.

```{r results = "asis"}
source("R/resample_data_script.R", echo = TRUE)
```
<br>
**Note** using `echo = TRUE` prints everything run and `include = TRUE` in the code snippet header prints the code iswell

# Varying sites and grids  {.tabset}

Here is a applied example of using dynamic tabs to represent a collection of plots. This can also be done with other R objects such as tables.

```{r, echo = FALSE, warning= FALSE, message=FALSE, results = "asis"}
my_data <- mtcars

#original example
p_list <- list()
p1 <- qplot(mpg, disp, data = my_data[1:10,])
p2 <- qplot(disp, mpg, data = my_data[10:20,])
p1 <- ggplot(my_data[1:10,], aes(x = disp, y = mpg))+
  geom_point()
p_list[[1]] <- list(p1, "First Plot")
p_list[[2]] <- list(p2, "Second Plot")

#demo using data in repo
p_list <- list()

for (i in 1:length(levels(ged.min$site))){
  ppt <- ggplot(ged.min[ged.min$site == levels(ged.min$site)[i] ,], 
                    aes(y = siteR, x = year)) +
        geom_point() +
        geom_point() +
        geom_line() +
        facet_grid(site ~ grid.id) +
        theme_bw() + 
     theme(axis.text.x = element_text(angle = 90))
 
    p_list[[i]] <- list(ppt, levels(ged.min$site)[i])
    } #i

#key to make this work is results = "asis" in code chunk
for (i in seq_along(p_list)){
 tmp <- p_list[[i]]
 #change level of tabing here :)
 cat("##", tmp[[2]], "\n")
 print(tmp[1])
 cat('\n\n')
}

```

# Another randomisation {.tabset}

Should be a difference and could be a good simple start to simulating differences between sites and grids given the observed differences in the sample data. This was originally what I thought would be helpful last time I bumped into you. Hopefully it helps. :)

```{r, echo = FALSE, warning= FALSE, message=FALSE, results = "asis"}
# run resampling R script
#can look at how simple this is in source()
#resample_data_script.R
datresampled1 <- read_csv("data/random_ged_resample1.csv") %>%
            mutate(site = factor(site))
#demo using data in repo
p_list <- list()

for (i in 1:length(levels(datresampled1$site))){
  ppt <- ggplot(datresampled1[datresampled1$site == levels(datresampled1$site)[i] ,], 
                    aes(y = n, x = year)) +
        geom_point() +
        geom_point() +
        geom_line() +
        facet_grid(site ~ grid.id) +
        theme_bw()+ 
     theme(axis.text.x = element_text(angle = 90))
 
    p_list[[i]] <- list(ppt, levels(datresampled1$site)[i])
    } #i

#key to make this work is results = "asis" in code chunk
for (i in seq_along(p_list)){
 tmp <- p_list[[i]]
 #change level of tabing here :)
 cat("##", tmp[[2]], "\n")
 print(tmp[1])
 cat('\n\n')
}

```
