---
title: "Updating the OpenWeather data for R"
delete_merged_file: yes
---

## Setup

First of all you have to store your API key in an environment variable called `OWM_API_KEY`.
For the current session this can be done with:

```{r eval = TRUE}
# OWM_API_KEY
# Sys.setenv(OWM_API_KEY = OWM_API_KEY)
```

## Get data

Due to the `...` parameter in R you can pass all parameters defined in the [openweathermap-api-reference](https://openweathermap.org/api) to the functions fetching data.

```{r eval = TRUE, message = FALSE}

library(owmr)

current <- get_current("Canberra", units = "metric", lang = "en")
class(current)

forecast <- get_forecast("Canberra", units = "metric")
# class(forecast)

cbr <- search_city_list("Canberra")

current_multiple <- find_cities_by_geo_point(
  cbr$lat,
  cbr$lon,
  cnt = 5,
  units = "metric"
)
class(current_multiple)

# bbox_greater_london <- c(-0.489, 51.28, 0.236, 51.686, 10)
# current_greater_london <- find_cities_by_bbox(bbox_greater_london)
# class(current_greater_london)
# current_greater_cbr %>% owmr_as_tibble() %>%
#   .[, c(columns, "name")]
```

## Get similar-ish data frames with `owmr_as_tibble`

```{r eval = TRUE}

columns <- c("dt_txt", "temp","pressure", "humidity" ,"temp_min", "temp_max")

current %>% owmr_as_tibble() %>%
  .[, columns]
forecast %>% owmr_as_tibble() %>%
  .[1:4, columns]
current_multiple %>% owmr_as_tibble() %>%
  .[, c(columns, "name")]

```

### Actual temperature

```{r}

```


## Leaflet integration

```{r eval = TRUE}
cbr <- search_city_list("Canberra")

# Get data for 9 cities around cbr
owm_data <- find_cities_by_geo_point(
  lat = cbr$lat,
  lon = cbr$lon,
  cnt = 9,
  units = "metric"
) %>% owmr_as_tibble()

owm_data %<>% parse_columns(list(temp = round))
head(owm_data)

# Create a popup template
popup_tpl <- paste0(
  "<b>{{name}}</b></br>",
  "{{coord_lon}}, {{coord_lat}}</br>",
  "{{temp}}°C, ",
  "<i>{{weather_description}}</i>"
)

# Test it ...
popup_tpl %$$% owm_data %>% head(2)

library(leaflet)

leaflet(width = "100%") %>%
  addProviderTiles("CartoDB.DarkMatter") %>%
  add_weather(owm_data, icon = owm_data$weather_icon, template = popup_tpl)
```

Furthermore, you can add weather map layers from OpenWeatherMap to the `map` object via `add_owm_tiles`. For available layers see `owm_layers`.

### Weather icons

I will create a set of unique weather icons in the future. For now 

```{r}
owm_data$weather_icon
```

